Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-01-07 paper/paper.tex
pass on examples

Finally, \tname{} ranks the inferred rules according to heuristics
extracted from a database of existing \tname{} rules. One example
heuristic is \Fix{...informa um exemplo concreto que
  vc. usaram...}. Instead of traffic, this step looks for the
structure of existing rules. The list below shows the rule options for
the top-5 rules \tname{} produces for this attack.

>>>>

Finally, \tname{} ranks the inferred rules according to heuristics
extracted from a database of existing \tname{} rules. One example
heuristic is \Luc{Ataque "JBoss JMX Console Beanshell Deployer WAR Upload and Deployment Exploit"
. O payload do pacote é o seguinte:
\begin{figure}[H]
  \lstinputlisting[language=C,numbers=none,keywords={dsize,itype}]{adaptor-rule.suricata}
  \label{fig:rule-example}
\end{figure}

A partir disso produzimos uma regra com os seguintes contents:

\begin{figure}[H]
  \lstinputlisting[language=C,numbers=none,keywords={dsize,itype}]{adaptor-contents-splitted.suricata}
  \label{fig:rule-example}
\end{figure}

Depois da etapa da minimização, as top 5 regras são:

\begin{figure}[H]
  \lstinputlisting[language=C,numbers=none,keywords={dsize,itype}]{adaptor-top5-rules.suricata}
  \label{fig:rule-example}
\end{figure}

A regra de ouro é:

\begin{figure}[H]
  \lstinputlisting[language=C,numbers=none,keywords={dsize,itype}]{adaptor-golden-rule.suricata}
  \label{fig:rule-example}
\end{figure}

}

\Fix{...informa um exemplo concreto que
  vc. usaram...}. Instead of traffic, this step looks for the
structure of existing rules. The list below shows the rule options for
the top-5 rules \tname{} produces for this attack.
